Topic Modeling of News

### 2017-10-27 paper/R/01_prepare.Rmd
explore model

```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

@@

# a list in which each element is one of your original JSON files
myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
#myJSON <- lapply(june, function(x) fromJSON(file=x))

length(myJSON)
```

@@

```{r, eval=FALSE, include=FALSE}
site <- NULL
title <- NULL
text <- NULL
published <- NULL
section <- NULL

fb_shares <- NULL
fb_likes <- NULL
fb_comments <- NULL
gplus_shares <- NULL
linkedin_shares <- NULL
stumbledupon_shares <- NULL

@@

  gplus_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["gplus"][[1]][["shares"]])
  linkedin_shares <- append(gplus_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["linkedin"][[1]][["shares"]])
  stumbledupon_shares <- append(stumbledupon_shares, myJSON[[i]]["thread"][[1]]["social"][[1]]["stumbledupon"][[1]]["shares"][[1]])

  external_links <- append(external_links, length(myJSON[[i]]["external_links"][[1]]))

@@

df <- cbind(site, title, text, published, section, fb_shares, fb_likes, gplus_shares, external_links)
df <- data.frame(df, stringsAsFactors = FALSE)
```

```{r}
rm(site, title, text, published, fb_shares, fb_likes, section, external_links)
```

## Clean Data
```{r}
df %>%
  mutate(fb_shares = as.numeric(fb_shares),
         fb_likes = as.numeric(fb_likes),
         gplus_shares = as.numeric(gplus_shares),
         external_links = as.numeric(external_links)) -> df
```

@@

```{r, eval=FALSE, include=FALSE}
# Save file
save(df, linkedin_shares, file="../output/news_cleaned.Rda")
```

## Save by Site
```{r}
df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/stern.csv")
df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/focus.csv")
df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/zeit.csv")
df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/wdr.csv")
df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/spiegel.csv")
df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/welt.csv")
df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/handelsblatt.csv")
df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/tagesschau.csv")
df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/swr.csv")
df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/bild.csv")
df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/ndr.csv")
```

## Load by site
```{r}
focus <- read.csv("../output/focus.csv")
#spiegel <- read.csv("../output/spiegel.csv")
#bild <- read.csv("../output/bild.csv")

df_reduced <- rbind(focus, spiegel, bild)
```

```{r}
save(df_reduced, file="../output/df_reduced")
```

>>>>

```{r}
rm(list = ls())

@@

# a list in which each element is one of your original JSON files
myJSON <- lapply(c(june,july,aug,sep), function(x) fromJSON(file=x)) 
```

@@

```{r}
site <- NULL
title <- NULL
text <- NULL
published <- NULL
section <- NULL

fb_shares <- NULL
fb_likes <- NULL
fb_comments <- NULL

@@

@@

df <- cbind(site, title, text, published, section, fb_shares, fb_likes, fb_comments)
df <- data.frame(df, stringsAsFactors = FALSE)
```

```{r}
rm(site, title, text, published, fb_shares, fb_likes, section, fb_comments)
```

## Clean Data
```{r}
df %>%
  mutate(fb_shares = as.numeric(fb_shares),
         fb_likes = as.numeric(fb_likes),
         fb_comments = as.numeric(fb_comments)) -> df
```

@@

```{r}
# Save file
save(df, file="../output/news_cleaned.Rda")
```

### 2017-10-27 paper/R/05_lda_eight2late.Rmd
explore model

load("../output/news_cleaned2.Rda")
write.csv(btw, file="../output/btw.csv")

@@

>>>>

load("../output/news_cleaned2.Rda")

@@

## Explore the model
```{r}
load(file ="../output/models/LDAGibbs 50 .Rda")
```

### Most likely Topics per Article
```{r}
# The topics function from the package is used to extract the most likely topic for each document 
btw.topics <- topics(ldaOut, 3)

# Create Dataframe
doctopics.df <- as.data.frame(t(btw.topics))

doctopics.df %>%
  transmute(ArticleID = rownames(.),
            Topic1 = V1,
            Topic2 = V2,
            Topic3 = V3) -> doctopics.df

doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)
doctopics.df[1:10,]

# Add Topic to origian DF
```

### Most likely Words per Topic
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)
btw.terms[1:5,1:10]
```

### Create Topic Labels
As part of the visualization I will construct later, a topic label needs be used to created. The terms are gathered in rank order and then the label is created by concatenating the first three terms.

```{r}
topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

topicTerms <- topicTerms %>% mutate(Topic = stringr::word(Topic, 2))
topicTerms$Topic <- as.numeric(topicTerms$Topic)

topicLabel <- data.frame()
for (i in 1:50){
  z <- dplyr::filter(topicTerms, Topic==i)
  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
  topicLabel <- rbind(topicLabel, l)
}
colnames(topicLabel) <- c("Label")

topicLabel
```

### Working with Theta (Topic prevalence)
```{r}
theta <- as.data.frame(posterior(ldaOut)$topics)
head(theta)
```

```{r}
x <- as.data.frame(row.names(theta), stringsAsFactors = FALSE)
#colnames(x) <- c("ArticleID")
#x$ArticleID <- as.numeric(x$ArticleID)

#theta2 <- cbind(x,theta)
```

```{r}
library(corrplot)

c <- cor(theta)
corrplot(c, method = "circle")
```
